Experience Report: Haskell in Computational Biology

### 2012-03-08 mrfy_experience_report.tex
spelling

Finally, one last barrier we faced was debugging runtime errors.
Runtime errors in the form of out-of-bounds indexing were particularly 
difficult to track down because they were not accompanied by a stack trace.
(While profiling with GHC could help remedy this, profiling was itself a 
barrier, as previous mentioned.)
We had to resort to polluting our code with cals to the \texttt{trace} function 
in order to track down where the out-of-bounds errors were occurring.

>>>>

Finally, one last barrier we faced was debugging runtime errors.
Runtime errors in the form of out-of-bounds indexing were particularly 
difficult to track down because they were not accompanied by a stack trace.
(While profiling with GHC could help remedy this, profiling was itself a 
barrier, as previously mentioned.)
We had to resort to polluting our code with calls to the \texttt{trace} function 
in order to track down where the out-of-bounds errors were occurring.
